---

title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
Sys.setlocale("LC_ALL","C")
activity<-read.csv("activity.csv",colClasses=c("integer","Date","integer"))
summary(activity)
```

## What is mean total number of steps taken per day?
```{r}
hist(tapply(activity$steps,activity$date,sum,na.rm=TRUE),main = "Number of steps per day",xlab = "Number of steps",breaks = 10)
```


## What is the average daily activity pattern?
```{r}
plot(tapply(activity$steps,activity$interval,mean,na.rm=TRUE),type="l",xlab="Interval",ylab="Mean number of steps")
names(which.max(tapply(activity$steps,activity$interval,mean,na.rm=TRUE)))
```

Mean and median number of steps
```{r}
mean(tapply(activity$steps,activity$date,sum,na.rm=TRUE))
median(tapply(activity$steps,activity$date,sum,na.rm=TRUE))
```


## Imputing missing values
Missing values:
```{r}
sum(is.na(activity))
```
Replacing missing values with the mean number of steps during that interval over all dates.
```{r}
meanstep<-tapply(activity$steps,activity$interval,mean,na.rm=TRUE)
meanstep<-array(meanstep,nrow(activity))
meanstep<-meanstep[is.na(activity)]
activity$steps<-replace(activity$steps,which(is.na(activity$steps)),meanstep)
hist(activity$steps,xlab="Steps",main="Steps per interval")
```

Mean and median after replacing missing values
```{r}
mean(tapply(activity$steps,activity$date,sum))
median(tapply(activity$steps,activity$date,sum))
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
library(lattice)
activity$weekdays<-ifelse(weekdays(activity$date) %in% c('Saturday','Sunday'),"weekend","weekday")
aggActivity<-aggregate(steps~interval*weekdays,activity,mean)
xyplot(steps~interval|weekdays,aggActivity,type="l")
```

We see that there are a differnce.